---
title: "Lars Schöbitz - CV"
format:
  typst:
    output-file: cv.pdf
    papersize: a4
    margin:
      x: 1.6cm
      y: 1.6cm
    fontsize: 10pt
    include-in-header: assets/typst-helpers.typ
execute:
  echo: false
  warning: false
  message: false
knitr:
  opts_chunk:
    dev: "ragg_png"
---

```{r setup}
#| fig.keep: "none"
knitr::opts_chunk$set(fig.keep = "none")
source("R/cv_functions.R")
cv <- create_cv()
```

```{r intro, results='asis'}
print_text_block(cv, "intro")
```

View this CV online at [www.lse.de](https://www.lse.de).

```{r band, results='asis'}
print_band(cv)
```

# Work Experience {data-icon="laptop"}

```{r work, results='asis'}
print_section(cv, "work_experience")
```

# Education {data-icon="graduation-cap"}

```{r education, results='asis'}
print_section(cv, "education")
```

# Open Data & Software {data-icon="database"}

```{r open-data, results='asis'}
print_section(cv, "open_data_software")
```

# Teaching {data-icon="chalkboard-teacher"}

```{r teaching, results='asis'}
print_section(cv, "teaching", style = "compact")
```

# Workshops {data-icon="users"}

```{r workshops, results='asis'}
print_section(cv, "workshops", style = "compact")
```

# Talks {data-icon="microphone"}

```{r talks, results='asis'}
print_section(cv, "talks", style = "compact")
```

# Blog & Writing {data-icon="pen-nib"}

```{r blog, results='asis'}
print_section(cv, "blog", style = "compact")
```

# Publications {data-icon="book"}

```{r publications, results='asis'}
print_section(cv, "publications")
```

# Conference Papers {data-icon="file-lines"}

```{r conf-papers, results='asis'}
print_section(cv, "conference_papers")
```

# Technical Reports {data-icon="bookmark"}

```{r reports, results='asis'}
print_section(cv, "technical_reports")
```

# Grants & Funding {data-icon="hand-holding-dollar"}

```{r grants, results='asis'}
print_section(cv, "grants")
```

# Awards {data-icon="trophy"}

```{r awards, results='asis'}
print_section(cv, "awards")
```

# Professional Roles {data-icon="award"}

```{r roles, results='asis'}
print_section(cv, "professional_roles")
```
