---
title: "Lars Schöbitz - CV"
pagetitle: "Lars Schöbitz - CV"
format:
  html:
    theme: [default, cv.scss]
    toc: false
    include-in-header:
      text: |
        <link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/font-awesome/6.5.1/css/all.min.css">
        <script async defer data-domain="lse.de" src="https://plausible.io/js/plausible.js"></script>
  typst:
    papersize: a4
    margin:
      x: 1.6cm
      y: 1.6cm
    fontsize: 10pt
    include-in-header: typst-helpers.typ
execute:
  echo: false
  warning: false
  message: false
knitr:
  opts_chunk:
    dev: "ragg_png"
---

```{r setup}
#| fig.keep: "none"
knitr::opts_chunk$set(fig.keep = "none")
source("R/cv_functions.R")
cv <- create_cv("data")
```

```{r intro, results='asis'}
print_text_block(cv, "intro")
```

::: {.content-visible when-format="html"}
[<i class="fa-solid fa-download"></i> Download this CV as a PDF](https://raw.githubusercontent.com/larnsce/cv/main/cv.pdf){.download-link}
:::

::: {.content-visible when-format="typst"}
View this CV online with clickable links at [lse.de/cv](https://www.lse.de/cv).

```{r band, results='asis'}
print_band(cv)
```

:::

::: {.content-visible when-format="html"}
::: {.cv-sidebar}

## Contact {.contact}

```{r contact, results='asis'}
print_contact(cv)
```

## Technical Skills {.skills}

```{r tech-skills, results='asis'}
print_skills(cv, "technical")
```

## Languages {.skills}

```{r skills, results='asis'}
print_skills(cv, "language")
```

:::
:::

# Work Experience {data-icon="laptop"}

```{r work, results='asis'}
print_section(cv, "work_experience")
```

# Education {data-icon="graduation-cap"}

```{r education, results='asis'}
print_section(cv, "education")
```

# Open Data & Software {data-icon="database"}

::: aside
```{r oda-aside, results='asis'}
print_text_block(cv, "open_data_aside")
```
:::

```{r open-data, results='asis'}
print_section(cv, "open_data_software")
```

# Teaching {data-icon="chalkboard-teacher"}

::: aside
```{r teach-aside, results='asis'}
print_text_block(cv, "teaching_aside")
```
:::

```{r teaching, results='asis'}
print_section(cv, "teaching", style = "compact")
```

# Workshops {data-icon="users"}

```{r workshops, results='asis'}
print_section(cv, "workshops", style = "compact")
```

# Talks {data-icon="microphone"}

```{r talks, results='asis'}
print_section(cv, "talks", style = "compact")
```

# Publications {data-icon="book"}

```{r publications, results='asis'}
print_section(cv, "publications")
```

# Conference Papers {data-icon="file-lines"}

```{r conf-papers, results='asis'}
print_section(cv, "conference_papers")
```

# Technical Reports {data-icon="bookmark"}

```{r reports, results='asis'}
print_section(cv, "technical_reports")
```

# Professional Roles {data-icon="award"}

```{r roles, results='asis'}
print_section(cv, "professional_roles")
```

# References {data-icon="address-book"}

```{r references, results='asis'}
print_section(cv, "references")
```
